NoTitle

### 2017-06-05 SpringerLNCS/sections/Formalization.tex
Conclusion.

Finally, (T-INTF) defines interface type-checking in a straightforward way.

@@

\subsection{Small-step Semantics and Congruence}
Figure ? and Figure ? define small-step semantic rules and congruence rules,
respectively. When evaluating an expression, they are invoked recursively and
alternately to produce a single value in the end. The small-step semantics (S-INVK), (S-PATHINVK) and (S-SUPERINVK) behave similarly, each corresponds to
one kind of method invocation. They all invoke \mbody for method body lookup. Generally, one can understand $\mbody(m, I, J)$ in a way that it finds the most specific body of method $m$, when the receiver has dynamic type $I$ and static type $J$.
The three rules require that the receiver and the arguments have been evaluated into values, before substitution is applied.

@@

$\mbody(m, I_d, I_s)$, as defined in Figure~\ref{fig:auxfunc}, denotes a method body lookup function.
We use $I_d, I_s$, since $\mbody$ is usually invoked by a receiver of a method $m$, with its dynamic
type $I_d$ and static type $I_s$. Such a function returns the most specific method implementation, more
accurately, its parameters, returned expression and the types. It considers both originally defined methods and method updates, so $\mostSpecific$ and $\mostSpecific_2$ are invoked.

@@

\begin{itemize}
	\item Syntax + typing rules + Semantics + Auxiliary definitions
	\item Implementation: a simple type checker + interpreter in Scala
\end{itemize}

\subsubsection{A Non-Trivial Example}

\begin{lstlisting}
interface A extends {
	A m() override A {return new A(); }
}
interface B extends A {
	A m() override B {return new B(); }
}
interface C extends A {
	A m() override C {return new C(); }
}
interface D extends B, C {
	A m() override B {return new D(); }
}
interface E extends B {
	A m() override B {return new E(); }
}
interface F extends D, E {
	A m() override B {return new F(); } 
	A n(B b) override F {return b.m(); }
}
new F().n(new F())
\end{lstlisting}

\begin{comment}
\[
\begin{array}{l}
\kwinterface \; A \; \kwextends \; \{ \\
\; \; \; \; A \; m() \; \kwoverride \; A \; \{\kwreturn \; \new A;\} \\
\} \\
\\
\kwinterface \; B \; \kwextends \; A \; \{ \\
\; \; \; \; A \; m() \; \kwoverride \; B \; \{\kwreturn \; \new B;\} \\
\} \\
\\
\kwinterface \; C \; \kwextends \; A \; \{ \\
\; \; \; \; A \; m() \; \kwoverride \; C \; \{\kwreturn \; \new C;\} \\
\} \\
\\
\kwinterface \; D \; \kwextends \; B, \; C \; \{ \\
\; \; \; \; A \; m() \; \kwoverride \; B \; \{\kwreturn \; \new D;\} \\
\} \\
\\
\kwinterface \; E \; \kwextends \; B \; \{ \\
\; \; \; \; A \; m() \; \kwoverride \; B \; \{\kwreturn \; \new E;\} \\
\} \\
\\
\kwinterface \; F \; \kwextends \; D, \; E \; \{ \\
\; \; \; \; A \; m() \; \kwoverride \; B \; \{\kwreturn \; \new F;\} \\
\; \; \; \; A \; n(B \; b) \; \kwoverride \; F \; \{\kwreturn \; b.m();\} \\
\} \\
\\
\new F.n(\new F)
\end{array}
\]
\end{comment}

~\red{Unfortunately I think this example shows that it is hard to reuse
	$D.m$ on path $B$ and $E.m$ on path $B$ in $F$?}

\red{We can use the $\kwsuper$ keyword to access the originally defined methods
	in super types, but we cannot access the old updating methods.}

\red{Just like $\kwsuper.I::m()$ is equivalent to $\new I.m()$, maybe we can add
a degree of freedom to $\kwsuper$, for example, $\kwsuper.D::B::m()$ is equivalent to
$\new D.B::m()$, so we can use $\kwsuper.D::B::m()$ and $\kwsuper.E::B::m()$ inside interface $F$ for code reuse?}

Interfaces $A,B,C,D,E,F$ OK in type checking.

To type-check $\new F.n(\new F)$:
\begin{itemize}
	\item By (T-INVK), we need to calculate $\mtype(n, F)$.
	\item $\mtype(n, F) = B \to A$. And $\new F : B$.
	\item $\new F.n(\new F) : A$.
\end{itemize}

~

To compute \red{$\new F.n(\new F)$}:
\begin{itemize}
	\item By (C-RECEIVER), we compute \red{$\new F$}:
		\begin{itemize}
			\item By (C-STATICTYPE): \red{$<F> \new F$}.
		\end{itemize}
	\item By (C-ARGS), we compute \red{$\new F$}:
		\begin{itemize}
			\item By (C-STATICTYPE): \red{$<F> \new F$}.
		\end{itemize}
	\item Now we get \red{$(<F> \new F).n(<F> \new F)$}. By (S-INVK):
		\begin{itemize}
			\item Compute $\mbody(n, F, F) = \red{(B \; b, A \; b.m())}$.
			\item Replace \red{$b$} with \red{$<B> \new F$} in \red{$b.m()$}.
			\item Replace \red{$\kwthis$} with \red{$<F> \new F$} in \red{$b.m()$}.
		\end{itemize}
	\item Finally we get \red{$<A>((<B> \new F).m())$}.
	\item By (C-FREDUCE), we first compute \red{$(<B> \new F).m()$}:
		\begin{itemize}
			\item By (S-INVK), we compute \red{$\mbody(m, F, B)$}.
			\item In $\mbody$, we invoke \red{$\mostSpecific(m, F, B)$}.
			\item In $\mostSpecific$, \red{$set = \{B\}$, $\prune(set) = \{B\}$}.
			\item Back to $\mbody$, we invoke \red{$\mostSpecific_3(m, F, B)$}.
			\item In $\mostSpecific_3$, \red{$set = \{B,D,E,F\}$, $\prune(set) = \{F\}$}.
			\item Back to $\mbody$, we check \red{$F.m$} and return \red{$(-,A \; (\new F))$}.
			\item Back to (S-INVK).
			\item Replace \red{$\kwthis$} with \red{$<B> \new F$} in \red{$\new F$}.
			\item Finally we get \red{$<A> \new F$}.
		\end{itemize}
	\item Now we have \red{$<A>(<A> \new F)$}.
	\item By (C-ANNOREDUCE): \red{$<A> \new F$}.
\end{itemize}

\red{TODO: class encapsulation problem: interface A: m; interface B: m update A; interface C: m update B.}

>>>>

Finally, (T-INTF) defines interface type-checking in a straightforward way. Note that it is responsible for checking conflicted paths with a same source. As we illustrated in Section ?, such a case is disallowed for unambiguity.

@@

\subsection{Small-step Semantics and Congruence}
Figure ? and Figure ? define small-step semantic rules and congruence rules,
respectively. When evaluating an expression, they are invoked recursively and
alternately to produce a single value in the end. The small-step semantics (S-INVK), (S-PATHINVK) and (S-SUPERINVK) behave similarly, each corresponds to
one kind of method invocation. They all invoke \mbody{} for method body lookup. Generally, one can understand $\mbody(m, I, J)$ in a way that it finds the most specific body of method $m$, when the receiver has dynamic type $I$ and static type $J$.
The three rules require that the receiver and the arguments have been evaluated into values, before substitution is applied.

@@

\red{H: mtype based on mbody?}
$\mbody(m, I_d, I_s)$, as defined in Figure~\ref{fig:auxfunc}, denotes a method body lookup function.
We use $I_d, I_s$, since $\mbody$ is usually invoked by a receiver of a method $m$, with its dynamic
type $I_d$ and static type $I_s$. Such a function returns the most specific method implementation, more
accurately, its parameters, returned expression and the types. It considers both originally defined methods and method updates, so $\mostSpecific$ and $\mostSpecific_2$ are invoked.

@@
